A cross-benchmark comparison of Learning to Rank methods

### 2014-05-16 cikm_paper/paper.tex
ndcg5 in meestertabel

\section{Raw Data on Normalised Winning Number for cross-comparison}
\label{app:norm_winnum_all}
\onecolumn
\begin{table*}\centering
\begin{longtable}{@{}rrrrrrrrrrrrrrrrr@{}}\toprule
& \multicolumn{2}{p{0.5cm}}{NDCG@3} & \phantom{a} 
& \multicolumn{2}{c}{NDCG@5} & \phantom{a} 
& \multicolumn{2}{c}{NDG@10} & \phantom{a} 
& \multicolumn{2}{c}{MAP}    & \phantom{a}
& \multicolumn{3}{c}{CROSS}\\
\cmidrule{2-3} \cmidrule{5-6} \cmidrule{8-9} \cmidrule{11-12} \cmidrule{14-16}
Method & NWN & \#ds && NWN & \#ds && NWN & \#ds && NWN & \#ds && WM & IWN & NWN \\ \midrule
AdaRank-MAP & 0.3486 & 12 && 0.3884 & 12 && 0.3648 & 13 && 0.3206 & 12 && 332 & 937 & 0.3543 \\
\bottomrule
\end{longtable}
\caption{Caption}
\end{table*}

>>>>

\section{Raw Data on Normalised Winning Number for cross-comparison}
\label{app:norm_winnum_all}
\onecolumn
\begin{longtable}{@{}rrrrrrrrrrrrrrrrr@{}}\toprule
& \multicolumn{2}{p{0.5cm}}{NDCG@3} & \phantom{a} 
& \multicolumn{2}{c}{NDCG@5} & \phantom{a} 
& \multicolumn{2}{c}{NDG@10} & \phantom{a} 
& \multicolumn{2}{c}{MAP}    & \phantom{a}
& \multicolumn{3}{c}{CROSS}\\
\cmidrule{2-3} \cmidrule{5-6} \cmidrule{8-9} \cmidrule{11-12} \cmidrule{14-16}
Method & NWN & \#ds && NWN & \#ds && NWN & \#ds && NWN & \#ds && WM & IWN & NWN \\ \midrule
AdaRank-MAP & 0.3486 & 12 && 0.3884 & 12 && 0.3648 & 13 && 0.3206 & 12 && 332 & 937 & 0.3543 \\
AdaRank-NDCG & 0.3073 & 12 && 0.3259 & 12 && 0.3158 & 16 && 0.2863 & 12 && 293 & 951 & 0.3081 \\
ADMM & - & - && - & - && & && & && & & \\
ApproxAP & - & - && - & - && & && & && & & \\
ApproxNDCG & 0.7949 & 1 && 0.7500 & 1 && & && & && & & \\
BagBoo & 0.8478 & 2 && 0.8400 & 1 && & && & && & & \\
Best Single Feature & - & - && - & - && & && & && & & \\
BL-MART & 0.9524 & 2 && 0.7200 & 1 && & && & && & & \\
BoltzRank-Pair & 0.8333 & 4 && 0.8350 & 4 && & && & && & & \\
BoltzRank-Single & 0.7549 & 4 && 0.7184 & 4 && & && & && & & \\
BT & 0.7273 & 3 && 0.7879 & 3 && & && & && & & \\
C-CRF & - & - && 0.9500 & 2 && & && & && & & \\
CA & - & - && - & - && & && & && & & \\
CCRank & - & - && - & - && & && & && & & \\
CoList & 1.0000 & 1 && - & - && & && & && & & \\
Consistent-RankCosine & - & - && - & - && & && & && & & \\
DCMP & 0.5459 & 9 && 0.5079 & 9 && & && & && & & \\
DirectRank & - & - && - & - && & && & && & & \\
EnergyNDCG & 0.3636 & 2 && 0.3778 & 2 && & && & && & & \\
FBPCRank & 0.4146 & 3 && 0.5529 & 3 && & && & && & & \\
FenchelRank & 0.7742 & 5 && 0.7500 & 5 && & && & && & & \\
FocusedBoost & 0.3750 & 2 && 0.4545 & 2 && & && & && & & \\
FocusedNet & 0.4583 & 2 && 0.6364 & 2 && & && & && & & \\
FocusedSVM & 0.2500 & 2 && 0.2727 & 2 && & && & && & & \\
FP-Rank & - & - && 0.9000 & 1 && & && & && & & \\
FRank & 0.3085 & 11 && 0.2849 & 10 && & && & && & & \\
FSMRank & 0.8333 & 4 && 0.8776 & 4 && & && & && & & \\
FSM$^{SVM}$ & 0.2292 & 2 && 0.4082 & 4 && & && & && & & \\
GAS-E & 0.3750 & 4 && 0.4694 & 4 && & && & && & & \\
GP & - & - && - & - && & && & && & & \\
GPRank & 0.8710 & 3 && 0.7253 & 3 && & && & && & & \\
GRankRLS & - & - && - & - && & && & && & & \\
GroupCE & 0.7312 & 3 && - & - && & && & && & & \\
GroupMLE & 0.5269 & 3 && - & - && & && & && & & \\
IntervalRank & 0.5897 & 1 && 0.3750 & 1 && & && & && & & \\
IPRank & 0.9355 & 3 && 0.8132 & 3 && & && & && & & \\
KeepRank & - & - && - & - && & && & && & & \\
Kernel-PCA RankBoost & - & - && 0.2857 & 3 && & && & && & & \\
KL-CRF & 0.5946 & 2 && 0.5789 & 2 && & && & && & & \\
LAC-MR-OR & - & - && - & - && & && & && & & \\
LambdaMART & 0.5714 & 2 && - & - && & && & && & & \\
LambdaNeuralRank & 1.0000 & 1 && 1.0000 & 1 && & && & && & & \\
LambdaRank & 0.2000 & 1 && 0.2000 & 1 && & && & && & & \\
LARF & 0.9892 & 3 && 0.9890 & 3 && & && & && & & \\
Linear Regression & 0.0714 & 9 && 0.1099 & 9 && & && & && & & \\
ListMLE & 0.0000 & 1 && - & - && & && & && & & \\
ListNet & 0.4495 & 12 && 0.4911 & 12 && & && & && & & \\
ListReg & 0.7312 & 3 && 0.6923 & 3 && & && & && & & \\
LRUF & 0.9823 & 4 && 0.9817 & 4 && & && & && & & \\
MCP & - & - && - & - && & && & && & & \\
MHR & 0.7500 & 1 && 0.6000 & 1 && & && & && & & \\
MultiStageBoost & - & - && - & - && & && & && & & \\
NewLoss & 0.5161 & 3 && 0.4286 & 3 && & && & && & & \\
OWPC & 0.6500 & 6 && - & - && & && & && & & \\
PERF-MAP & 0.3894 & 4 && 0.2661 & 4 && & && & && & & \\
PermuRank & - & - && - & - && & && & && & & \\
Q.D.KNN & - & - && 0.3205 & 3 && & && & && & & \\
RandomForest & - & - && - & - && & && & && & & \\
Rank-PMBGP & - & - && 0.7692 & 1 && & && & && & & \\
RankAggNDCG & - & - && 0.5000 & 3 && & && & && & & \\
RankBoost & 0.3211 & 12 && 0.2794 & 10 && & && & && & & \\
RankCSA & - & - && - & - && & && & && & & \\
RankDE & - & - && 0.5385 & 1 && & && & && & & \\
RankELM (pairwise) & 0.6154 & 1 && 0.6500 & 1 && & && & && & & \\
RankELM (pointwise) & 0.6923 & 1 && 0.7000 & 1 && & && & && & & \\
RankMGP & - & - && - & - && & && & && & & \\
RankNet & 0.1887 & 1 && 0.2857 & 3 && & && & && & & \\
RankRLS & - & - && - & - && & && & && & & \\
RankSVM & 0.3010 & 12 && 0.3613 & 11 && & && & && & & \\
RankSVM-Primal & 0.3920 & 8 && 0.4509 & 8 && & && & && & & \\
RankSVM-Struct & 0.3520 & 9 && 0.4136 & 9 && & && & && & & \\
RCP & - & - && 0.5758 & 3 && & && & && & & \\
RE-QR & - & - && - & - && & && & && & & \\
REG-SHG-SDCG & 0.3846 & 1 && 0.4500 & 1 && & && & && & & \\
Ridge Regression & 0.4088 & 7 && 0.3333 & 7 && & && & && & & \\
RSRank & 0.5729 & 4 && 0.5306 & 4 && & && & && & & \\
SmoothGrad & - & - && - & - && & && & && & & \\
SmoothRank & 0.6038 & 7 && 0.6340 & 7 && & && & && & & \\
SoftRank & 0.2308 & 1 && 0.2750 & 1 && & && & && & & \\
sortNet & 0.2500 & 2 && 0.5147 & 4 && & && & && & & \\
SparseRank & 0.8224 & 4 && 0.8173 & 4 && & && & && & & \\
SVD-RankBoost & - & - && 0.2727 & 3 && & && & && & & \\
SVM$^{MAP}$ & 0.2893 & 7 && 0.3801 & 8 && & && & && & & \\
SwarmRank & - & - && 0.1538 & 1 && & && & && & & \\
TGRank & 0.5417 & 4 && 0.6122 & 4 && & && & && & & \\
TM & 0.5909 & 3 && 0.7576 & 3 && & && & && & & \\
VFLR & - & - && - & - && & && & && & & \\
\bottomrule
\caption{Raw data of cross-benchmark comparison}
\label{tab:raw_data}
\end{longtable}
